Git Learning Notes

### 2014-08-01 ch-moox/moox.tex
after a long pause
moo3 draft 50%

Molybdenum oxides \ce{MoO3} crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3})exhibits anisotropic structure with strong bonding along [001] and [100] direction while Van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion\cite{Sian2005}. This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photoabsorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerenes\cite{Li2003c}, and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the Van der Waals heterostructures.\cite{Geim2013}

In this thesis, we developed a new method to prepare \ce{MoO3} by using alkaline oxides as catalysts. This newly discovered a vapor-liquid-solid growth mechanism produced two new \ce{MoO3} structures: long nanoribbons and microscale towers. We then investigated the phase and crystalline structures of these new morphologies, and demonstrated the application in photocatalyst and electrochromic devices.

\section{Synthesis and Properties of Molybdenum Oxides}

\subsection{Growth of molybdenum oxides}

Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures. We will not try to exhaust these efforts since it has been well summarized in several review articles.\cite{He2003} So we only gave a brief introduction here. Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches. \citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}. Both methods have its own merits. Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; while vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time. Both methods are scalable for industrial applications. However the hydrothermal treatment seems to allow more  nanostructures control than do the vapor deposition method. Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one. The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures. \citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of MB under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0eV$. Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$).

In spite of these numerous growth of \ce{MoO3}, we point out that reports on VLS mechanism and other than Si substrates are still scarce. We will explore these relative new domains and present our results in Sec.~\ref{sec:result}.

\subsection{Crystal structures and chemical features of molybdenum oxides}

@@

While considering the fact that four of the six surrounding O atom are at distances from 1.67\AA to 1.95\AA, while the remaining two are as far as 2.25 and 2.33\AA, \ce{MoO3} could be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis. The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane. Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This also stress that the \ce{MoO6} octahedra are rather distorted.

Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of Mo-O or W-O ensembles in comparison to cations of other elements. And no mixing of vibrations of the cationic sublattices with that of \ce{Mo-O} or \ce{W-O} lattices. So the structural features of \ce{Mo-O} or \ce{W-O} polyhedra are dominating factors affecting the vibration frequencies and thermodynamic values of the molybdates and tungstates.\cite{Fomichev1992}

\begin{table}[htb]
\centering
\caption{Crystal structures of alkali metal molybdates and tungstates}\label{tab:naxmow}
\begin{tabular}{llr}
\toprule
formula & structure  & remarks  \\
\midrule
\ce{A2O}:\ce{MO3}\textsuperscript{\emph{a}} & isolated tetrahedral \ce{MO4} anions& \\
\ce{A2O}:\ce{2MO3} & chain-type anions of \ce{MO4} and \ce{MO6} & \\
\ce{A2O}:\ce{3MO3} & chain-type anions of \ce{MO5} and \ce{MO6} & \\
\ce{A2O}:\ce{4MO3} & chain-type anions of \ce{MO6} & \\
\bottomrule

@@

Raman band assignment for \ce{A2MO4} is well grounded. Alkali metal cations with octahedral coordination occur below 230 $cm^{-1}$. For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.

Molybdenum bronze also exhibits intriguing features, for instance, charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} is side=centered monoclinic phase, with lattice parameter $a=18.249$\AA, $b=7.561$\AA, $c=9.856$\AA, and $\beta=117.54$ at RT. \ce{K0.3MoO3} presents a semiconductor-to-metal transition at 180 K. Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000. Along this high conducting axis, metallic reflection behavior is confirmed by optical measurements. Therefore, this blue bronze $\ce{K_{0.3}MoO3}$ is known as quasi-1D metal.\cite{Sing1999}

\subsection{Synthesis methods in this theis}

@@

\textbf{Substrate treatment.} Silicon substrates(p-$\langle100\rangle$, University Wafers) were first cut into 10mm by 25mm pieces and ultrasonically cleaned with acetone and ethanol for 15 minutes(Branson 1510R-MTH), each followed by blow-drying with nitrogen gas. Then the substrates were selectively treated in an oxygen plasma cleaning apparatus(Kurt J Lesker: Plasma-Preen 862, 2Torr) for 3 minutes to increase the wettability. The substrates without plasma cleaning were rendered as hydrophobic. Finally, the substrate was drop-cast 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) and naturally left dry in a convection hood with a flask cover above. Other alkaline ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass(Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping. Mica was cleaved right before growth without other treatment.

\textbf{Synthesis.} In a typical synthesis (Fig.~\ref{fig:mooxgrowth}), molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet. With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 minutes and lasted for 15 to 120 minutes. Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature. The receiving substrate was placed in downstream location where the temperature was about 400 to 670 \si{\degreeCelsius} according to open air temperature profile. To observe the formation of droplets, clean silicon substrate was coated with 9 nm molybdenum film using a magnetron sputter(Desk IV TSC, Denton Vacuum), followed by \ce{NaOH} dipping as described before. Then the substrate was placed into chamber for growth, where all the parameters remained unchanged except the absence of Mo powder source.

\textbf{Materials characterization.} The morphology and composition of the as-synthesized samples were analyzed by scanning electron microscopy (SEM,JEOL JSM-6480) and energy dispersive X-ray spectroscopy (EDS,Oxford Instrument INCA). Crystal structures were characterized using X-ray diffraction (XRD, PANXpert X’pert Pro MRD with Cu $K\alpha$ radiation at $\lambda$=1.5418\AA) and transmission electron microscopy (TEM, JEOL JEM-2100 \ce{LaB6} operated at 200kV). Optical measurements were performed by Micro-Raman spectroscopy (Horiba Scientific, Labram HR800 with 532 nm excitation laser) in a confocal microscope backscattering configuration with spectral resolution about 1 cm$^{-1}$. Optical absorption spectra was recorded using UV-Vis-NIR spectrophotometer(Schimadzu, UV2600Plus) in transmission mode. The as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol for 15 seconds. The dispersion was left for 12 hrs to enable the possible sedimentation, after which became transparent under the unaided eye. Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing ethanol only.

\section{Discussion on molybdenum oxides}\label{sec:result}

In vapor synthesis process, two growth mechanism exists: VS and VLS. VS process is widely accepted for the growth of \ce{MoO3}. Yet we caution that synthesis conditions should be scrutinized to determine the exact mechanism. \citeauthor{Li2002c} suggested a VS mechanism at 700 \si{\degreeCelsius} and VLS at 750 \si{\degreeCelsius} and higher.\cite{Li2002c} \citeauthor{Fibers2007} proposed a modified VS mechanism probably because the deposition occurs on \ce{Al2SiO5} with possible \ce{Al_{0.95}SiNa_{0.06}O_x} involved. Therefore temperature and possible impurity could potentially alter the growth mechanism. We divide the growth results into two categories: on Si substrate and on non-Si substrate, and describe them respectively. We also briefly mention using liquid exfoliation to prepare few layer \ce{MoO3}.

\subsection{Growth on Si substrates}

Mo began to be oxidized into \ce{MoO3} at 500 \si{\degreeCelsius}, \ce{MoO3} vapor pressure began to increase rapidly above 700 \si{\degreeCelsius}. \cite{Margrave1967} And the melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}. With these facts in mind, we design the experimental parameters as listed in Table.~\ref{tab:mooxsi}. We should point out that these parameters are selected and optimized from a wide range of combinations. And when we discuss the influence of one parameter with different values, one should assume other parameters still adapt those listed in Table.~\ref{tab:mooxsi}.

\begin{table}[htb]
\centering
\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
\begin{tabular}{lcccr}
\toprule
&&&\multicolumn{2}{c}{Flow (sccm)} \\
\cmidrule(l){4-5}
 & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure  & Ar & \ce{O2}  \\
\midrule
typical values  & 800    & 200mTorr & 10 & 10  \\
\end{tabular}
\end{table}

The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}. Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace. To facilitate discussion and provide a tight context, we define the position of substrate as the coordinate of its upper-stream edge along this temperature axis (i.e. the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}). The usual length of Si substrate is 1 inch. When positioned at 7 inch, it is then located in a temperature range of $650 \sim 350$ \si{\degreeCelsius}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[Growth setup of \ce{MoO3}]{Chemical vapor system and its temperature profile. The triangular labels $\blacktriangledown$ were measured points at ambient pressure. The nominal substrates temperature were estimated from interpolation data.}
\label{fig:mooxgrowth}
\end{figure}

From previous works,\cite{predeep2011} we found that with $T_h = 600$ and substrate placed at 6.5 inches, microflakes was found at the high temperature edge of Si, suggesting the nucleation already started.\footnote{020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates. This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{(31210-31510 batches)} We also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, i.e., the growth at upper stream edge first increase then decrease. This is not surprising when considering the temperature field requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}. Using conditions in Table.~\ref{tab:mooxsi} and 1 hr growth, we observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}. Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34\mu m$.

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.45\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.45\textwidth]{mosemsi_b}}
\caption[Representative morphologies of \ce{MoO3} on Si]{SEM images of representative depositions of \ce{MoO3} on Si. (a)Low magnification. (b) High magnification. }
\label{fig:mosisem}
\end{figure}

This rectangular shape implies the boundary plane along growth direction (long axis) is (001), in consistency with previous experimental reports\cite{Zeng1998,Li2002b} and theoretical studies.\cite{Firment1983,Cora1997} We also observed different shapes, i.e., elongated hexagonal using similar growth conditions. This is not an indication of different growth mode. It is a normal thermodynamic fluctuation. The growth rates along different crystalline direction of \ce{MoO3} are determined by the free surface energy. In fact, (201), (101) and (102) planes have all been observed as terminating planes.\cite{Zeng1998} The stacking rate of \ce{MoO6} octahedra along $a$ and $c$ axis could develop some other ratio. And the coexistence of different planes in one growth suggests the similarity of free surface energies between these surfaces. In other words, the migration barrier of adatoms on (010) plane is presumably much lower than that on other low index planes due to the Van der Waals interaction nature along [010] direction.

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532nm$.}
\label{fig:mooxch}
\end{figure}

As shown in Fig.~\ref{fig:mooxch}, the crystal structures and phase of as-synthesized samples were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628\AA, \emph{b}=13.855\AA, \emph{c}=3.6964\AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, we shall see a different scenario in Section.~\ref{sec:nasi}, where the orientation is changed.

>>>>

In this work, a new growth mechanism of molybdenum oxide (\ce{MoO3}) 1D structures was discovered, highlighted by \ce{MoO3} long nanobelts and micro-scale towers. The samples were synthesized using a group of alkaline metal based catalysts, including \ce{NaOH}, \ce{KI}, and \ce{Na2CO3}. In contrast to the sole axial growth found in the conventional catalyst-assisted growth, two different growth modes were observed for the \ce{MoO3} 1D growth here: transverse growth and axial growth. In the transverse mode, the 1D structures grow perpendicularly to the catalyst-deposition interface with catalyst particles on the side surfaces; whereas in the axial mode, the crystal grows along the catalyst-deposition axis. The growth modes were explained by a modified vapor-solid-solid (VSS) mechanism, and factors that affect the growth were explored in details.

This remaining sections are organized as following: a brief review on previous studies of \ce{MoO3} is given first, followed is the synthesis method in this dissertation. Emphasis will be placed on morphological and crystal structure characterization of 1D \ce{MoO3} nanostructures, and the verification of proposed VSS mechanism. This chapter is concluded with a summary of VSS growth and some preliminary results of morphology controlled \ce{MoO3} nanostructures.

\section{Synthesis and Properties of Molybdenum Oxide}

Molybdenum oxide (\ce{MoO3}) crystallizes in three phases, orthorhombic $\alpha$-\ce{MoO3}, monoclinic $\beta$-\ce{MoO3} and the metastable hexagonal h-\ce{MoO3}.\citep{Deb1968,Fibers2007} $\alpha$-\ce{MoO3} phase (hereafter \ce{MoO3}) exhibits anisotropic structure with strong bonding along [001] and [100] direction while van der Waals interaction along [010] direction.\cite{He2003} Due to this unique structure, \ce{MoO3} was found to have several important properties and a wide range of technological applications, such as electrochromism and photochromism,\cite{Yao1992} lubricants,\cite{Sheehan1996} photocatalysts,\cite{Chen2010} and gas sensor, including \ce{CO},\cite{Comini2005} \ce{NO2},\cite{Taurino2006} \ce{H2}\cite{Sha2009} and ethanol.\cite{Choopun} Moreover, other features arise when nanoscale \ce{MoO3} is specifically prepared, for instance, field emission.\citep{Li2002d,Zhou2003b}  As a layered hosting material, \ce{MoO3} can be further modified by intercalating with alkaline ions\citep{Spahr1995,Li2006b,Hu2011} and even divalent ion.\cite{Sian2005} This structural richness have enabled improved performance in Li-ion\cite{Mai2007} and sodium-ion battery.\cite{Hariharan2013} In combination with \ce{TiO2} forming a core-shell structure, these nanoparitcles are reported to lower the photon absorption energy of \ce{TiO2}.\cite{Elder2000} When combined with Ag as layered structure, transparent conducting behavior was observed.\cite{Nguyen2012} In addition, \ce{MoO3} is a good precursor for preparing other useful materials, such as \ce{MoS2} fullerene\cite{Li2003c} and few layer \ce{MoS2}.\cite{Lin2012} It will also be an important member of the van der Waals heterostructures.\cite{Geim2013}

\subsection{Growth of molybdenum oxide}

Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures. Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}. Both methods have its own merits. Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; while vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time. Both methods are scalable for industrial applications. However the hydrothermal treatment seems to allow more  nanostructures control than do the vapor deposition method. Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one. The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures. \citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV. Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$). It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.

\subsection{Lattice structures of molybdenum oxide and molybdates}

@@

While considering the fact that four of the six surrounding O atom are at distances from 1.67 to 1.95 \AA, while the remaining two are as far as 2.25 and 2.33 \AA, \ce{MoO3} could also be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis. The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane. Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This view stresses that the \ce{MoO6} octahedra are rather distorted. A brief summary of crystallography, band structure and dielectric function is listed in Appendix.

It is known that a series of molybdate compound forms when alkali metal ions are incorporated into the \ce{MoO3} lattice, and the structures are summarized in Table.~\ref{tab:naxmow}. Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of \ce{Mo-O} ensembles in comparison to cations of other elements. And no mixing of vibrations of the cationic sublattices with that of \ce{Mo-O} lattices is anticipated. So the structural features of \ce{Mo-O} polyhedra are dominating factors affecting the vibration frequencies and thermodynamic values of the molybdates.\cite{Fomichev1992}

\begin{table}[htb]
\centering
\caption{Crystal structures of alkali metal molybdates and tungstates}\label{tab:naxmow}
\begin{tabular}{llr}
\toprule
formula & structure  &  \\
\midrule
\ce{A2O}:\ce{MO3}\textsuperscript{\emph{a}} & isolated tetrahedral \ce{MO4} anions& \\
\ce{A2O}:\ce{2MO3} & chain-type anions of \ce{MO4} and \ce{MO6} & \\
\ce{A2O}:\ce{3MO3} & chain-type anions of \ce{MO5} and \ce{MO6} & \\
\ce{A2O}:\ce{4MO3} & chain-type anions of \ce{MO6} & \\
\bottomrule

@@

Raman band assignment for \ce{A2MO4} is well grounded. Alkali metal cations with octahedral coordination occur below 230 cm$^{-1}$. For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.

Molybdenum bronze also exhibits intriguing features, for instance, charge-density-wave states\footnote{In CDW states, conductivity is non-Ohmic above a threshold electric field.} was found in blue bronze \ce{K_{0.3}MoO3}, which can be prepared by electrolytic reduction of \ce{K2MoO4} and \ce{MoO3} melt.\cite{Dumas1983} \ce{K_{0.3}MoO3} stay as monoclinic phase at room temperature, with lattice parameter $a=18.249$ \AA, $b=7.561$ \AA, $c=9.856$ \AA, and $\beta=117.54$, and exhibits a semiconductor-to-metal transition at 180 K. Electrical transport measurements yield an highly anisotropic ratio of DC conductivities of 1:10:1000. Along this high conducting axis, metallic reflection behavior is confirmed by optical measurements. Therefore, this blue bronze $\ce{K_{0.3}MoO3}$ is known as quasi-1D metal.\cite{Sing1999}

\subsection{Synthesis methods in this thesis}\label{sec:grow}

@@

\textbf{Substrate treatment.} Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}. To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast and then naturally left dry in a convection hood. Other alkaline ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping. Mica was cleaved right before growth without other treatment.

\textbf{Synthesis.} In a typical synthesis (Fig.~\ref{fig:mooxgrowth}), molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet. With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 minutes and lasted for 15 to 120 minutes. Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature. The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile. To observe the formation of droplets, clean silicon substrate was coated with 9 nm molybdenum film using magnetron sputtering, followed by \ce{NaOH} dipping as described before. Then the substrate was placed into chamber for growth, where all the parameters remained unchanged except the absence of Mo powder source. Non-catalytic growth shares the same procedure except the Si substrate treatment.

\section{Results and Discussion on Molybdenum Oxide}\label{sec:result}

In this section, the growth of \ce{MoO3} on Si was presented first, followed by catalytic growth, both of which were characterized by SEM, XRD, TEM and EDX. Then the catalytic growth mechanism was investigated using \ce{NaOH} treated Si substrate.
\subsection{Growth on Si substrates}\label{sec:nonsi}

The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}. Based on these data, the growth was designed with parameters listed in Table.~\ref{tab:mooxsi}. It is worth mentioning that these parameters are selected and optimized from a wide range of combinations. And when the influence of one parameter is studied, the others are fixed.
%growth parameter
\begin{table}[htb]
\centering
\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
\begin{tabular}{lcccr}
\toprule
&&&\multicolumn{2}{c}{Flow (sccm)} \\
\cmidrule(l){4-5}
 & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure (mTorr) & Ar & \ce{O2}  \\
\midrule
Typical values  & 800    & 200 & 10 & 10  \\
\bottomrule
\end{tabular}
\end{table}

The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}. Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace. To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis (i.e. the substrate location is 7 in in Fig.~\ref{fig:mooxgrowth}). The usual length of Si substrate is 1 in. When positioned at 7 in, it is then located in a temperature range of $650 \sim 350$ \si{\degreeCelsius}.
% cvd layout
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[Growth setup of \ce{MoO3}]{Chemical vapor system and its temperature profile. The triangular labels $\blacktriangledown$ were measured points at ambient environment. The nominal substrates temperature were estimated from interpolation data.}
\label{fig:mooxgrowth}
\end{figure}

From previous works in our group,\cite{predeep2011} the author found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates. This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm.\footnote{(31210-31510 batches)} The author also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease. This is not surprising when considering the temperature field requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}. Using conditions in Table.~\ref{tab:mooxsi} and 2 h growth, the author observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}. Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34$  $\mu m$.
% sem
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.45\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.45\textwidth]{mosemsi_b}}
\caption[Representative morphologies of \ce{MoO3} on Si]{(a) Low magnification and (b) high magnification SEM images of representative depositions of \ce{MoO3} on Si for non-catalytic growth.}
\label{fig:mosisem}
\end{figure}

As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of as-synthesized samples were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, \emph{c}=3.6964 \AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, a different XRD peak pattern is observed in Sec.~\ref{sec:nasi}, where the catalytic growth occurs.
% xrd raman
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{(a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
\label{fig:mooxch}
\end{figure}

The Raman spectrum of as-synthesized specimens also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively. The 667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral. The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table.~\ref{tab:moram}.
% raman assign
\begin{table}[htb]
\centering
\caption{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work(\si{cm^{-1}}) & Sym.       &          & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Growth on NaOH-Si substrate}\label{sec:naohsi}
